Understanding the impacts of video-guided activities on parent-child interaction

### 2019-07-04 paper/cogsci2019/cogsci2019.Rmd
graph improvements, updated results

```{r libraries, include=F}
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
source("multiplot.R")

@@

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from Kinedu (Kinedu Inc.), a parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to the video group or the control group; parents in the video group watched a video from the Kinedu app (matched to their child's age), and then performed the activity with their child using the props from the video. 
Parents in the control group did not watch a Kinedu video, but were given a set of the same age-appropriate props and asked to play with their infants as they would at home.

@@

lmer_data <- d %>%
  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         video = as.factor(video))

a <- d$gender == "F"
length(a[a == TRUE])

```

### Participants. 
`r nrow(d)` infants (F = 42, M = 18) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California. 
We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2). 
61% of participants (n = 37) had been exposed to two or more languages as indicated by their parent. 
Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5). 
Fifteen parents reported that their child was of Hispanic origin. 
Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 6), four-year college (n = 14), some graduate school (n = 1), to completed graduate school (n = 28) or declined to state (n = 6).

@@

Participants were randomly assigned to either the *Video* condition or the *Control* condition. 
Parents participating in the Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the Control condition watched no activity video, and were simply asked to play with their child as they normally would.
The Control condition was yoked to the Activity Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the Control condition received the same props but did not watch the activity video.
Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
The EPAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.

@@

```{r, e1-lexdiv-regressions, echo=F, include=F}
# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
modTTR <- lmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
summary(modTTR) # condition -0.123 t(39.9) = 4.25 p<.001

modMTLD <- lmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
summary(modMTLD) # condition -11.67 t(43) = 3.08 p=.004 !! singular fit
# Bayesian regression (stan_glmer in rstanarm) shows the same

# predict word tokens
tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=lmer_data)
summary(tokens_mod) # condition 57.23 t(34.4) = 2.19 p<.05

# predict word types
types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data) # !! singular fit
summary(types_mod) # nothing
```

We fit a mixed-effects linear regression predicting TTR as a function of condition, age (scaled and 0-centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4]. 
There was significantly lower TTR in the Video condition (mean: 0.32) than in the Control condition (mean: 0.43, $\beta=-.12$, t(39.9) = 4.25, *p*<.001). 
There were no significant effects of age, gender, or parent's level of education.
A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean: 15.7) than in the Control condition (mean: 21.9, $\beta=-11.67$, t(43) = 3.08, *p*<.01), with no other significant effects.
Figure 1 shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=57.23$, t(34.4)=2.19, *p*<.05), with parents using more words in the Video condition (mean: 225, 95% CI: [197,252]) than in the Control condition (mean: 165, 95% CI: [139,193]).

(Table with mean and SD of tokens, types, and TTR)

```{r e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1. Error bars show bootstrapped 95 percent confidence intervals (CIs)."}
d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))

# all at once, but there are NAs in SD cols ?
e1 <- d %>% group_by(Condition) %>%
  summarise(TTR=mean(TTR), TTRsd=sd(TTR),
            MTLD=mean(MTLD), MTLDsd=sd(MTLD),
            types=mean(types), types.sd=sd(types),
            tokens = mean(tokens), tokens.sd=sd(tokens))

ms_lex <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col="TTR") # Type/Token Ratio

ttr_means <- d%>%
  group_by(Condition)%>%
  summarise(mean = mean(TTR), sd = sd(TTR))

e1ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

ms_lex_mtld <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col="MTLD")

mtld_means <- d %>%
  group_by(Condition)%>%
  summarise(mean = mean(MTLD), sd=sd(MTLD))

# report table with mtld_means

e1mtld <- ggplot(ms_lex_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

@@

```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 1."}
ms_tok <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "tokens")

e1tokens <- ggplot(ms_tok, aes(x=Condition, y = mean, fill = Condition)) +geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

ms_type <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "types")

e1types <- ggplot(ms_type, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Total Number of Word Types") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

@@

```{r, e1-effect-size, echo=F}
cohens_d <- diff(ttr_means$mean) / (sqrt(sum(ttr_means$sd^2)) / 2)
```

@@

lmer_data <- d %>%
  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(Condition = factor(Condition), 
         bids_tot = as.numeric(bids_tot),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         Video = as.factor(Video))

@@

# Total number of bids
bids_mod <- lmer(paste("bids_tot", model_string), data = lmer_data)
summary(bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01, gender p=.05 ?

bid_cond <- lmer_data %>% group_by(Condition) %>% 
  summarise(mean = mean(bids), sd = sd(bids)) 
print(bid_cond)

@@

# Episodes of passive joint attention.
pja_mod <- lmer(paste("pja", model_string), data = lmer_data)
summary(pja_mod) # marginal RR, beta=-1.07 p=.07, condition*RR beta=1.83 p<.05

@@

We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (scaled and 0-centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. This lme4 model included random intercepts per video. 
There were significantly more bids for JA in the Video condition (mean: 6.24, sd: 2.79) than in the Control condition (mean: 3.56, sd: 2.50, $\beta=3.51$, t(40.3) = 2.95, *p*<.01). 
There were no other significant effects.
Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=1.83$, t(41.5) = 2.22, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
Figure X shows ... by condition.

```{r e1ja-graphs, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of bids and episodes of Joint Attention in Experiment 1."}

ms_bids <- d %>% group_by(Condition) %>%
  multi_boot_standard(col="bids_tot")

e1bids <- ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  xlab("Condition") + ylab("Total Bids for Joint Attention") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

# total joint attention episodes
ms_tja <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "total_ja")

e1tja <- ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

@@

```{r e1ja-graphs-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Average number of passive and coordinated episodes of JA in Experiment 1."}
ms_pja <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "pja")

e1pja <- ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Episodes of Passive Joint Attention")  +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")

#Episodes of coordinated joint attention
ms_cja <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "cja")

e1cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Episodes of Coordinated Joint Attention")  +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (Type/Token ratio and MTLD) was higher when parents were just asked to play as they normally would.
This may suggest that parents in the Video condition are being more repetitive in their attempt to stick to the task prescribed in the video.
Demographics and EPAQ do not interact with condition, but there is a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).

There was a main effect of condition on total bids for joint attention. 
Parents in the Video condition, after seeing a video demonstrating an activity, made a greater number of bids for joint attention with their child.
There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
There was a marginal effect of gender on bids for joint attention, with parents of males producing more bids. 
There was a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of PJA to a greater extent for people with high RR scores.
While the electronically-delivered parenting advice increased the number of bids for joint attention by parents, it did not significantly effect the number or duration of episodes of joint attention. 
It may be that child variables had a larger relative impact on the attainment of joint attention.

@@

Experiment 1 found that parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home. 
Parents who watched a Kinedu video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions ([link](https://osf.io/2bpdf/)).

@@

lmer_data <- d %>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD),
         TTR = as.numeric(TTR),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         video = as.factor(video))
```

>>>>

```{r libraries, include=F}
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(tidyboot)
library(knitr)
source("multiplot.R")

@@

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from Kinedu (Kinedu Inc.), a parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to the video condition or the control condition; parents in the _video_ condition watched a video from the Kinedu app (matched to their child's age), and then performed the activity with their child using the props from the video. 
Parents in the _control_ condition did not watch a Kinedu video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.

@@

lmer_data <- d %>%
  #filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         video = as.factor(video))

e1_gender = table(d$gender)
#table(cut_interval(d$age, n=2, breaks=c(.5,1.5,2.1), labels=F))
#table(cut_number(d$age, n=3, breaks=c(.5,1.5,2.1)))
e1_parent_ed = table(d$parent_ed)
```

### Participants. 
`r nrow(d)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California. 
We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2). 
62% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent. 
Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5). 
Fifteen parents reported that their child was of Hispanic origin. 
Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = `r e1_parent_ed[1]`), some college (n = `r e1_parent_ed[2]`), four-year college (n = `r e1_parent_ed[3]`), some graduate school (n = `r e1_parent_ed[4]`), to completed graduate school (n = `r e1_parent_ed[5]`).

@@

Participants were randomly assigned to either the *Video* condition or the *Control* condition. 
Parents participating in the Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the Control condition watched no activity video, and were simply asked to play with their child as they normally would.
The Control condition was yoked to the Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the Control condition received the same props but did not watch the activity video.
Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
The EPAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.

@@

```{r, e1-lexdiv-regressions, echo=F, include=F}
get_lmer_reporting_values <- function(lmer.fit, digits=2) {
  Vcov <- vcov(lmer.fit, useScale = FALSE)
  beta <- round(fixef(lmer.fit), digits)
  se <- round(sqrt(diag(Vcov)), digits)
  zval <- round(beta / se, digits)
  pval <- round(2 * pnorm(abs(zval), lower.tail = FALSE), 4)
  # not sure how to pull estimated degrees of freedom...
  return(cbind(beta, se, zval, pval))
}
require("lmerTest")
# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
modTTR <- lmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
summary(modTTR) # condition:Exp -0.113 t(52.4) = 4.22 p<.001
e1TTR = get_lmer_reporting_values(modTTR)

modMTLD <- lmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
summary(modMTLD) # condition -8.73 t(55) = 2.67 p=.001 !! singular fit
e1MTLD = get_lmer_reporting_values(modMTLD)
# Bayesian regression (stan_glmer in rstanarm) shows the same:
require("rstanarm")
bmodMTLD <- stan_glmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
summary(bmodMTLD) # condition mean=-8.7 sd=3.3 2.5%=-15.1 97.5%=-20

# predict word tokens
tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=lmer_data) # only 54 parents completed the EPAQ
summary(tokens_mod) # condition 56.02 t(40.4) = 2.30 p<.05
e1tokens = get_lmer_reporting_values(tokens_mod)

# predict word types
types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data) # !! singular fit
summary(types_mod) # nothing (hint: conditionexp:AA beta=19.04 p=.11)
e1types = get_lmer_reporting_values(types_mod) 
# verify with Bayesian regression:
bmod_types <- stan_glmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data)
summary(bmod_types)

e1_lexdiv <- lmer_data %>% group_by(condition) %>%
  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
```

We fit a mixed-effects linear regression predicting TTR as a function of condition, age (scaled and 0-centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4]. 
There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp","beta"]`, t(52.4) = `r e1TTR["conditionexp","zval"]`, *p*<.001). 
There were no significant effects of age, gender, or parent's level of education.
A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`, $\beta=$`r e1MTLD["conditionexp","beta"]`, t(55) = `r e1MTLD["conditionexp","zval"]`, *p*=.001), with no other significant effects.
Figure \ref{fig:e1lex_div} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

```{r e1tokens, echo=F, include=F}
d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))

ms_lex_mtld <- d %>% group_by(Condition) %>%
  tidyboot_mean(MTLD) 
ms_lex <- d %>% group_by(Condition) %>%
  tidyboot_mean(TTR) # Type/Token Ratio
ms_tok <- d %>% group_by(Condition) %>%
  tidyboot_mean(tokens) 
ms_type <- d %>% group_by(Condition) %>%
  tidyboot_mean(types)
```

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta= `r e1tokens["conditionexp","beta"]`$, t(40.4)=`r e1tokens["conditionexp","zval"]`, *p*<.05), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="Control")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Control")$ci_upper, 0)`]).

```{r tab1, echo=FALSE}
e1 <- d %>% group_by(Condition) %>%
  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
            "Mean types"=mean(types), types.sd=sd(types),
            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
names(e1) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.")
```

```{r fig:e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1lex_div} Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1. Error bars show bootstrapped 95 percent confidence intervals (CIs)."}

e1ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

e1mtld <- ggplot(ms_lex_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=MTLD), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

@@

```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 1."}

e1tokens <- ggplot(ms_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=tokens), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

e1types <- ggplot(ms_type, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=types), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Number of Word Types") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

@@

```{r, e1-effect-size, echo=F, include=F}
cohens_d <- function(dat) {
  return( diff(dat$mean) / (sqrt(sum(dat$sd^2)) / 2) )
}

ttr_means <- d %>% group_by(Condition) %>%
  summarise(mean = mean(TTR), sd = sd(TTR))
cohens_d(ttr_means) # -1.68
```

@@

lmer_data <- d %>%
  filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>%
  mutate(Condition = factor(Condition), 
         bids_tot = as.numeric(bids_tot),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         Video = as.factor(Video))

@@

# Total number of bids
bids_mod <- lmer(paste("bids_tot", model_string), data = lmer_data)
summary(bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01, gender p=.05 ?
e1bids = get_lmer_reporting_values(bids_mod)

e1bids_M <- lmer_data %>% group_by(Condition) %>% 
  summarise(mean = mean(bids), sd = sd(bids))

@@

# Episodes of passive joint attention.
pja_mod <- lmer(paste("pja", model_string), data = lmer_data)
summary(pja_mod) # marginal RR, beta=-1.07 p=.07, condition*RR beta=1.83 p<.05
e1pja = get_lmer_reporting_values(pja_mod)

@@

We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (scaled and 0-centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
This lme4 model included random intercepts per video. 
There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="Control")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Control")$sd,2)`, $\beta=`r e1bids["ConditionVideo","beta"]`$, t(40.3) = `r e1bids["ConditionVideo","zval"]`, *p*<.01). 
There were no other significant effects.
Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=1.83$, t(41.5) = 2.22, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
Figure X shows ... by condition.

```{r fig:e1ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja} Mean number of bids (left) and episodes (right) of joint attention by condition in Experiment 1."}

ms_bids <- d %>% group_by(Condition) %>%
  tidyboot_mean(bids_tot)

e1bids <- ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=bids_tot), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Bids for Joint Attention") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

# total joint attention episodes
ms_tja <- d %>% group_by(Condition) %>%
  tidyboot_mean(total_ja)

e1tja <- ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

@@

```{r fig:e1ja-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja-pass-coord} Average number of passive and coordinated episodes of JA in Experiment 1."}
ms_pja <- d %>% group_by(Condition) %>%
  tidyboot_mean(pja)

e1pja <- ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=pja), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Episodes of Passive Joint Attention") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")

#Episodes of coordinated joint attention
ms_cja <- d %>% group_by(Condition) %>%
  tidyboot_mean(cja)

e1cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=cja), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Episodes of Coordinated Joint Attention")  +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (Type/Token ratio and MTLD) was higher when parents were just asked to play as they normally would.
This may suggest that parents in the Video condition end up being more repetitive in their attempt to stick to the task prescribed in the video.
Demographics and EPAQ do not interact with condition, although there was a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).

There was a main effect of condition on total bids for joint attention. 
Parents in the Video condition, after seeing a video demonstrating an activity, made a greater number of bids for JA with their child.
There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
There was a marginal effect of gender on bids for JA, with parents of males producing more bids. 
There was a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of passive JA to a greater extent for people with high RR scores.
While the electronically-delivered parenting advice increased the number of bids for joint attention by parents, it did not significantly effect the number or duration of episodes of joint attention. 
It may be that child variables had a larger relative impact on the attainment of joint attention.

@@

Experiment 1 found that parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home. 
Parents who watched a Kinedu video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^3]

[^3]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/).

@@

lmer_data <- d %>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD),
         TTR = as.numeric(TTR),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         video = as.factor(video))

e2_gender = table(d$gender)
e2_ethnicity = table(d$ethnicity)
e2_parent_ed = table(d$parent_ed)
```
